---
title: "Project 2"
author: "Kate Sheafor and Amy Portillo-Ramirez"
date: "11/08/2021"
output: html_document
---
Conditionals
  If less than X ratings
Loop
  Colors
Function
  No :)
  
```{r}
library(ggplot2)
books<- read.csv("books.csv")
books$num_pages <- as.numeric(books$num_pages)
books$average_rating <- as.numeric(books$average_rating)
```

original code
```{r}
ggplot(books, aes(x= average_rating)) + geom_histogram(stat="bin", binwidth = 0.05, fill="cornflowerblue",color="black") + xlab("Average Rating (0-5)") + ylab("Number of Ratings (millions)")
```

assigning colors og
```{r}
colors <- c(0:5)

assign.colors <- function(color.in){
color <- switch(color.in,
  "red" = r,
  "yellow"= y,
  "green"= g
  )
return(assign.colors)
}
```

colors: ave rating <2 red
```{r}
library(ggplot2)
r<-books$average_rating<=2.5
y<-books$average_rating>2.5
g<-books$average_rating>4
rating <- c("last", "average", "first")
color<- c("red", "yellow", "green")

###function###
bad=head(books$average_rating)
rank(bad,ties.method = "last")
average=head(books$average_rating)
rank(average,ties.method = "average")
best=head(books$average_rating)
rank(best, ties.method = "first")

###conditional###
x<-books$average_rating
graphcolor <- function(x)
  if (x=="last") {
    color=="red"
    } else if (x=="average"){
             color=="yellow"
    } else if (x=="good"){
               output <-color=="green"
      }
###GRAPH###
ggplot(books, aes(x= average_rating),y= ratings_count) + geom_histogram(stat="bin", binwidth = 0.05, fill="red",color="black") + xlab("Average Rating (0-5)") + ylab("Number of Ratings (millions)")
```
Amy's New Code That Works(ish)
```{r}
r<-books$average_rating<=2.5
g<-books$average_rating<=3.5
b<-books$average_rating>=3.6
ggplot(books, aes(x= average_rating)) + geom_histogram(stat="bin", binwidth = 0.05, fill=rgb(43, 228, 178, maxColorValue = 255),color="black") + xlab("Average Rating (0-5)") + ylab("Number of Ratings (millions)")
```


omit all ratings 100,000,000>
```{r}
ratingcount <- function(input){
  if (input==books$ratings_count)
    output <- omit(ratings_count>100000000)
      }

ggplot(books, aes(x= average_rating)) + geom_histogram(stat="bin", binwidth = 0.05, fill="cornflowerblue",color="black") + xlab("Average Rating (0-5)") + ylab("Number of Ratings (millions)")
```

